Presentation Title

### 2017-08-04 thesis/appendices/consensus-example.tex
Write more design variations
Write varying facilitator; describe proto example

\chapter{Consensus Example}
\label{app:consensus-example}

\begin{figure}[htb]
    \frame{\includegraphics[trim={0 0 0 11cm}, clip, width=1.0\textwidth]{trustchain-1}}
    \centering
    \caption{Initial state}
    \label{fig:trustchain-1}
\end{figure}

\begin{figure}[htb]
    \frame{\includegraphics[trim={0 0 0 8cm}, clip, width=1.0\textwidth]{trustchain-2}}
    \centering
    \caption{Initial state}
    \label{fig:trustchain-2}
\end{figure}

\begin{figure}
    \frame{\includegraphics[trim={0 0 0 2cm}, clip, width=1.0\textwidth]{trustchain-3}}
    \centering
    \caption{Initial state}
    \label{fig:trustchain-3}
\end{figure}

\begin{figure}
    \frame{\includegraphics[width=1.0\textwidth]{trustchain-4}}
    \centering
    \caption{Initial state}
    \label{fig:trustchain-4}
\end{figure}

>>>>

\chapter{Consensus example}
\label{app:consensus-example}

\begin{figure}[htb]
    \includegraphics[trim={0 0 0 11cm}, clip, width=1.0\textwidth]{trustchain-1}
    \centering
    \caption{We begin in a state where some facilitators $\F_{r-2}$ just agreed on the consensus result $\C_{r-1}$ but have not yet propogated it yet.}
    \label{fig:trustchain-1}
\end{figure}

\begin{figure}[htb]
    \includegraphics[trim={0 0 0 8cm}, clip, width=1.0\textwidth]{trustchain-2}
    \centering
    \caption{The facilitators propogates $\C_{r-1}$. Upon receiving it, the nodes perform two tasks;
    (1) elect new facilitators $\F_{r-1}$ by selecting the first $n$ nodes ordered by $\textsf{H}(\C_{r-1} || pk)$,
    and (2) create new CP blocks---$c_{a, 6}, c_{b, 4}$ and $c_{c, 8}$.
    $\textsf{H}(\cdot)$ is a cryptographically secure hash function and $pk$ is the public key of the respective node.}
    \label{fig:trustchain-2}
\end{figure}

\begin{figure}
    \includegraphics[trim={0 0 0 2cm}, clip, width=1.0\textwidth]{trustchain-3}
    \centering
    \caption{Nodes now send their new CP blocks to the new facilitators $\F_{r-1}$.
    While $\F_{r-1}$ is trying to reach consensus on a set of CP blocks,
    nodes carry on making transactions as usual (concurrently).
    We remark that the to-be-agreed consensus result $\C_r$ is created using CP blocks from the previous round---$c_{a, 6}, c_{b, 4}$ and $c_{c, 8}$.
    }
    \label{fig:trustchain-3}
\end{figure}

\begin{figure}
    \includegraphics[width=1.0\textwidth]{trustchain-4}
    \centering
    \caption{Finally, when $\F_{r-1}$ decides on $\C_r$ (which should contain $c_{a, 6}, c_{b, 4}$ and $c_{c, 8}$) and disseminates it.
    Nodes compute new facilitators $\F_{r}$ and create new CP blocks.}
    \label{fig:trustchain-4}
\end{figure}

### 2017-08-04 thesis/chapters/ch2-problem.tex
Write varying facilitator; describe proto example

Off-chain transaction systems are implemented using multi-signature addresses~\cite{bitcoinmultisig} and hashed time-locked Bitcoin contracts~\cite{bitcointimelock}.
In the simiplest case, 
if two parties wish to make transactions,
they open a payment channel in the form of of a multi-signature Bitcoin address (for two parties it would be a 2-of-2 signature address).
Each of the party must also deposit some Bitcoins in the multi-signature address.
Both parties keep the channel state which is not broadcasted to the network.
The state is updated when the two parties make new transactions.
The protocol disincentivises the parties from broadcasting old channel states.
If this issue occurs, the counterparty can drain all the Bitcoins in the channel.
After the payment channel is closed, the net transaction is broadcasted to the Bitcoin blockchain.
The two-party scheme can be extended to a network of channels,
which allows two parties to make off-chain transactions without an open channel as long as they are connected by nodes that do.

>>>>

Off-chain transaction systems are implemented using multi-signature addresses~\cite{bitcoinmultisig} and hashed time-locked Bitcoin contracts~\cite{bitcointimelock}.
In the simiplest case, 
if two parties wish to make transactions,
they open a payment channel in the form of of a multi-signature Bitcoin address (for two parties it would be a 2-of-2 signature address).
Each of the party must also deposit some Bitcoins in the multi-signature address,
this is called the opening transaction.
Both parties keep the channel state which is not broadcasted to the network.
The state is updated when the two parties make new transactions.
The protocol disincentivises the parties from broadcasting old channel states.
If this issue occurs, the counterparty can drain all the Bitcoins in the channel.
To close the channel, the parties simply boradcast the latest net settlement to the Bitcoin network,
this is called the closing transaction.
Effectively, only two transactions need to be broadcasted to the Bitcoin network---the opening and the closing transaction,
even if the two parties made thousands or millions of transactions in between.
The two-party scheme can be extended to a network of channels,
which allows two parties to make off-chain transactions without an open channel as long as they are connected by nodes that do.

### 2017-08-04 thesis/chapters/ch5-implementation.tex
Write varying facilitator; describe proto example

>>>>

\section{Communication cost with varying number of facilitators}
Up to this point we focused on the effect of communication cost, throughput and so on with respect to the population size.
In this section we consider a varying number of facilitators,
which gives us an insight on our system performance may perform when the number of facilitators are higher than 32.

\begin{figure}[tb]
  \centering
  \makebox[\linewidth][c]{%
  \begin{subfigure}[b]{0.7\textwidth}
    \includegraphics[width=\textwidth]{neighbour-fixed/consensus-communication-cost-vs-facilitators}
    \caption{Transactions are with fixed neighbours.}
    \label{fig:facilitators-comms-fixed}
  \end{subfigure}%
  \begin{subfigure}[b]{0.7\textwidth}
    \includegraphics[width=\textwidth]{neighbour-random/consensus-communication-cost-vs-facilitators}
    \caption{Transactions are with random neighbours.}
    \label{fig:facilitators-comms-random}
  \end{subfigure}
  }
  \caption{The communication cost of the consensus protocol increase polynomially with respect to the number of facilitators as expected from the ACS communication complexity.}
  \label{fig:facilitators-comms}
\end{figure}

\Cref{fig:facilitators-comms} shows the communication cost of the consensus protocol for varying numbers of facilitators.
There is strong evidence that the communication cost grows polynomially.
We expect this because of there are polynomial terms in the ACS communication complexity---$O(n^2|v| + \lambda n^3 \log n)$.
This also means that the rounds would take longer to complete and transactions would take longer to verify.
On the other hand, we get better fault tolerance.
Thus a linear increase in fault tolerance ($t$) costs a polynomial increase in communication cost.
